\documentclass[11pt,letterpaper,titlepage]{article}

\usepackage{geometry}
\geometry{left=2cm,right=2cm,top=2cm,bottom=3cm}

\usepackage{setspace}
\onehalfspacing

\usepackage{multicol}
\setlength{\columnsep}{3em}

\usepackage{booktabs}

\usepackage[table,x11names]{xcolor}

\usepackage{multirow}

\usepackage{pgfgantt}

\usepackage{listings}

\usepackage{xcolor}
\definecolor{vgreen}{RGB}{104,180,104}
\definecolor{vblue}{RGB}{49,49,255}
\definecolor{vorange}{RGB}{255,143,102}

\lstdefinestyle{C-style}
{
    language=C,
    basicstyle=\small\ttfamily,
    keywordstyle=\color{vblue},
    identifierstyle=\color{black},
    commentstyle=\color{vgreen},
    % numbers=left,
    numberstyle=\tiny\color{black},
    numbersep=11pt,
    tabsize=4,
    moredelim=*[s][\colorIndex]{[}{]},
    literate=*{:}{:}1
}

\lstdefinestyle{txt-style}
{
    basicstyle=\small\ttfamily,
    % numbers=left,
    numbersep=11pt,
    tabsize=4,
    moredelim=*[s][\colorIndex]{[}{]},
    literate=*{:}{:}1
}

\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, positioning, fit,calc}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
            
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\usepackage{pifont}

\usepackage[toc,page]{appendix}

\pagestyle{empty}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

\usetikzlibrary{mindmap,trees}
\usepackage{verbatim}

\usepackage{indentfirst}
\setlength{\parindent}{2em}

\usepackage{listings}

\usepackage{chngcntr}
\counterwithin{section}{part}
\renewcommand\thesection{\arabic{section}}

\usepackage{graphicx}

\usepackage{subcaption}

\usepackage{fancyhdr}

\pagestyle{fancy}
\lhead{}
\rhead{}
\lfoot{ECEN 749 Section 601 Lab 5}
\cfoot{\thepage}
\rfoot{@Lei Wang (Wilson)}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\headwidth}{\textwidth}
\renewcommand{\footrulewidth}{0.4pt}
\newcommand{\RomanNumeralCaps}[1]
    {\MakeUppercase{\romannumeral #1}}

\makeatletter
\newcommand*\@lbracket{[}
\newcommand*\@rbracket{]}
\newcommand*\@colon{:}
\newcommand*\colorIndex{%
    \edef\@temp{\the\lst@token}%
    \ifx\@temp\@lbracket \color{black}%
    \else\ifx\@temp\@rbracket \color{black}%
    \else\ifx\@temp\@colon \color{black}%
    \else \color{vorange}%
    \fi\fi\fi
}
\makeatother

\usepackage{trace}

\begin{document}

\begin{titlepage}
  \centering
	{\scshape\large Texas A\&M University \par}
	\vspace{1cm}
	{\scshape\Large Department of Electrical and Computer Engineering \par}
	\vspace{4cm}
    \vspace{0.5cm}
	{\huge\bfseries ECEN 749 Microprocessor System Design\par}
	\vspace{4cm}
	{\Large Lab 5 Report (Section 601)\par}
	\vspace{1cm}
	{\Large Student: Lei Wang (Wilson)\par}
	\vspace{1cm}
	{\Large UIN: 829009485\par}
	\vspace{1cm}
	{\Large Instructor: Dr. Paul V. Gratz\par}
	\vspace{4cm}
	\vfill

  % Bottom of the page
	{\large Submitted: February 25th, 2020 \par}

\end{titlepage}

\newpage

\tableofcontents{}

\newpage

\part{Introduction}

Lab 5 teaches how to write, compile, load and unload Linux kernels on the ZYBO Z7-10 board. The lab is an extension of the previous lab that teaches how to boot Linux from a micro-SD card. Lab 5 consists of building and using two Linux kernels: the hello-world kernel and the multiplier kernel that uses the multiplier IP created back a few labs before.

\part{Procedure}

\begin{enumerate}
    
    \item Preparation and test:
    
    \begin{enumerate}
        
        \item Create a new directory for this lab. Copy all the files from lab4. The sub-directories containing Linux and u-boot may be too large and take a long time to transfer. Leave those sub-directories out. We can bypass such issue by editing the relative path in the makefile.
        
        \item Copy the four files created in lab4 into the micro-SD card.
        
        \item Put the micro-SD card into the ZYBO Z7-10 board and power up the board. A successful boot should be indicated by the green LDE indicating ``programming done''.
        
        \item Run:
        
        \verb|source /opt/coe/Xilinx/Vivado/2015.2/settings64.sh|
        
        \verb|picocom -b 115200 -r -l /dev/ttyUSB1|
        
        \item Press the PS reset button and wait for console output in Picocom.
        
        \item Run:
        
        \verb|mount /dev/mmcb1k0p1 /mnt/|
        
        to mount the micro-SD card into the Linux file system.
        
        \item Run:
        
        \verb|cd /mnt/|
        
        \verb|ls -al|
        
        to check whether the micro-SD card has been properly mounted.
        
    \end{enumerate}
    
    \item The hello kernel:
    
    \begin{enumerate}
        
        \item Pop the micro-SD card after unmounting it and insert into the workstation in the lab. Keep the ZYBO Z7-10 board powered.
        
        \item Create a sub-directory in the lab5 directory named \textbf{module}.
        
        \item Place the \textbf{hello.c} file downloaded from the course website into the created sub-directory.
        
        \item In the same sub-directory, create a makefile with the content in appendix \ref{appendix:makefile_hello}
        
        \item Run:
        
        \verb|source /opt/coe/Xilinx/Vivado/2015.2/settings64.sh|
        
        \verb|make ARCH=arm CROSS COMPILE=arm-xilinx-linux-gnueabi-|
        
        to cross-compile the hello kernel.
        
        \item Copy the \textbf{hello.ko} file to the micro-SD card.
        
        \item Eject the micro-SD card. Insert into the ZYBO Z7-10 board and mount it to the file system.
        
        \item Run
        
        \verb|cd /mnt|
        
        to move to the directory that contains the compiled module.
        
        \item Run the following command to test for loading and unloading kernel modules:
        
        \begin{table}[ht]
        \centering
        \begin{tabular}{@{}lll@{}}
        \toprule
        Command & Comment                              & Example \\ \midrule
        \verb|insmod <module.ko>|        & Install the module                   & \verb|insmod hello.ko|        \\ \midrule
        \verb|lsmod|        & List the installed modules           & \verb|lsmod|        \\ \midrule
        \texttt{dmesg |tail}        & Show the Linux kernel buffer message &    \texttt{dmesg |tail}    \\ \midrule
        \verb|rmmod <module>|        & Remove the module from the kernel    &   \verb|rmmod hello|      \\ \bottomrule
        \end{tabular}
        \caption{Some Linux commands related to kernel modules.}
        \end{table}
        
        
        
        
        
        to see the output when installing the hello module.
        
    \end{enumerate}
    
    
    
\end{enumerate}

\newpage

\part{Results}



\newpage

\part{Conclusion}

\textbf{Q: Change thecurrent directory to `/mnt' using `cd' and examine the contents of the directory using `ls'. What do you see?}

A: The setting of the question is after the micro-SD card being unmounted. The output is nothing as the files in the micro-SD card no longer associates with the path \verb|/mnt|.

\textbf{Q: If prior to step 2.f, we accidentally reset the ZYBO Z7-10 board, what additional steps would be
needed in step 2.g?}

A: 

\textbf{Q: What is the mount point for the SD card on the CentOS machine?}

A:

\textbf{Q: If we changed the name of our hello.c file, what would we have to change in the Makefile? Likewise, if in our Makefile, we specified the kernel directory from lab 4 rather than lab 5, what
might be the consequences?}

A: 

\newpage

\begin{appendices}

\end{appendices}

\section{Makefile for hello.c}
\label{appendix:makefile_hello}
\lstinputlisting[style={txt-style}]{Makefile_hello}

\end{document}
